### 2014-11-12 minimax.tex
Fixed typos.
small edits for space

The code in Fig.~\ref{minimax:check-end} shows deals with expanding the tree.
The first three rules (lines 1-10) deal
with the case where no children nodes are created and the last three rules
(12-29) deal with the cases for creating new nodes.
The rule in lines 12-25 generates new nodes using the
\texttt{exists} language construct, which creates a child node 
\texttt{B}. We link \texttt{B} with its parent (\texttt{parent(B, A)})
and kick start the expansion of that node \texttt{B} by adding a \texttt{play}
fact.

As noted before in Section~\ref{sec:fifo}, the runtime schedules nodes by
default, which requires a complete expansion of the tree before computing the
scores at the leaves, leading
to a memory complexity of $\mathcal{O}(n)$, where $n$ is the number of nodes in
the tree.

@@

With coordination, we set the priority of a node to be its depth
so the tree is expanded in a depth-first fashion (lines 15 and 22),
leading to a memory complexity of $\mathcal{O}(d t)$, where $d$
is the depth of the tree and $t$ is the number of threads.
Since threads prioritize deeper nodes, the scores of the first leaves are immediatelly
computed and then sent to the parent node. At this point, the leaves are deleted
and reused for other nodes in the tree, resulting in minimal memory usage.

@@

\begin{topfig}
   \begin{center}
      \subfloat[]{\small\begin{tabular}[b]{ | c | c | c |}
         \hline                       
         \textbf{\# T} & \textbf{R} & \textbf{C} \\ \hline \hline
         1 & 11.80GB & 0.50MB \\ \hline
         2 & 12.19GB & 1.45MB \\ \hline
         4 & 13.82GB & 2.35MB \\ \hline
         8 & 14.87GB & 4.36MB \\ \hline
         16 & 13.79GB & 8.1MB \\ \hline
         \end{tabular}
         \normalsize
      }
      \subfloat[]{\includegraphics[width=4.5cm]{results/min-max-tictactoe.png}}
   \end{center}
   \scap{results:memory_minmax}{Memory usage and scalability of the regular and coordinated versions
      of MiniMax.}
\end{topfig}

>>>>

The code in Fig.~\ref{minimax:check-end} deals with expanding the tree.
The first three rules (lines 1-10) deal
with the case where no children nodes are created and the last three rules
(12-29) deal with the cases for creating new nodes.
The rule in lines 12-25 generates new nodes using the
\texttt{exists} language construct, which creates a child node 
\texttt{B}. We link \texttt{B} with its parent (\texttt{parent(B, A)})
and kick start the expansion of that node \texttt{B} by adding a \texttt{play}
fact.

As noted in \sectref{sec:fifo}, the default scheduler is
breadth-first, which in this case leads to a complete expansion of the
tree before computing the scores at the leaves.  This results in using
$\mathcal{O}(n)$ memory, where $n$ is the number of nodes in the tree.

@@

With coordination, we set the priority of a node to be its depth
so the tree is expanded in a depth-first fashion (lines 15 and 22),
leading to a memory complexity of $\mathcal{O}(d t)$, where $d$
is the depth of the tree and $t$ is the number of threads.
Since threads prioritize deeper nodes, the scores of the first leaves are immediately
computed and then sent to the parent node. At this point, the leaves are deleted
and reused for other nodes in the tree, resulting in minimal memory usage.

@@

\begin{topfig}
\vspace*{-2ex}
   \begin{center}
      \subfloat[]{\small\begin{tabular}[b]{ | c | c | c |}
         \hline                       
         \textbf{\# T} & \textbf{R} & \textbf{C} \\ \hline \hline
         1 & 11.80GB & 0.50MB \\ \hline
         2 & 12.19GB & 1.45MB \\ \hline
         4 & 13.82GB & 2.35MB \\ \hline
         8 & 14.87GB & 4.36MB \\ \hline
         16 & 13.79GB & 8.1MB \\ \hline
         \end{tabular}
         \normalsize
      }
      \subfloat[]{\includegraphics[width=4.5cm]{results/min-max-tictactoe.png}}
   \end{center}
   \scap{results:memory_minmax}{Memory usage and scalability of the regular and coordinated versions
      of MiniMax.}
\end{topfig}
